---
title: "Embedding D3 output in R Markdown"
output_dir: "outputs_delete"
output:
  html_document:
    includes:
      in_header: template_elements/doc_header.html
    self_contained: false
    keep_md: true
knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), "outputs_delete", 'outputs.html')) })

---


```{r setup, include=FALSE}
library(jsonlite)
knitr::opts_chunk$set(echo = TRUE)
```

Let's create a very basic d3 graph using data from R.  since the graph is d3, we will need the d3.js file for the graph to render.
<div id="q1" > </div>
```{r mybox1}
1+1
```

```{r mybox2}
```

```{r child='d3_child.Rmd'}
```


Plan:  Do a heirarchical data viewer.
Then do one with a map.

``` {r results='asis'}
# Each child is an object with a 'size', or an objeect with a list of children
# Algo: at each stage, generate a list of x children (say 2).  But each child is either a leaf, or a 
single_child <- function() {
  child <- list()
  child[["name"]] <- "a_child"
  child[["value"]] <- 1
  return(child)
}

create_children <- function() {
  children <- list()
  for (i in 1:4) {
    if (runif(1) < 0.2)  {
      children[[i]] <- list()
      children[[i]][["name"]] <- "a node"
      children[[i]][["children"]] <- create_children()
    } else {
      children[[i]] <- single_child()
    }
  }
  return(children)
}

tree <- list()
tree[["name"]] <- "head"
tree[["children"]] <- create_children()


# Make this into json


cat(sprintf("<script>  data = %s </script>", toJSON(tree, auto_unbox=TRUE)))
```

<div id="dendogram" > </div>
<style>

text {
  font: 10px sans-serif;
}

tspan:last-child {
  font-size: 9px;
  fill-opacity: 0.8;
}

.node rect {
  shape-rendering: crispEdges;
}

.node--hover rect {
  stroke: #000;
}

</style>
<script>
var svg = d3.select("#dendogram").append("svg").attr("height","500px").attr("width","100%");
width = "1000"
height = "500"
var format = d3.format(",d");

var color = d3.scaleMagma()
    .domain([-4, 4]);

root = d3.hierarchy(data).sum( function(d) { 
            return d.value ? 1 : 0;
        });
        
       
debugger;
//var stratify = d3.stratify()
//    .parentId(function(d) { return d.id.substring(0, d.id.lastIndexOf(".")); });

var treemap = d3.treemap()
    .size([width, height])
    .paddingOuter(3)
    .paddingTop(19)
    .paddingInner(1)
    .round(true);




  treemap(root);

  var cell = svg
    .selectAll(".node")
    .data(root.descendants())
    .enter().append("g")
      .attr("transform", function(d) { return "translate(" + d.x0 + "," + d.y0 + ")"; })
      .attr("class", "node")
      .each(function(d) { d.node = this; })
      .on("mouseover", hovered(true))
      .on("mouseout", hovered(false));

  cell.append("rect")
      .attr("id", function(d) { return "rect-" + d.id; })
      .attr("width", function(d) { return d.x1 - d.x0; })
      .attr("height", function(d) { return d.y1 - d.y0; })
      .style("fill", function(d) { return color(d.depth); });

  cell.append("clipPath")
      .attr("id", function(d) { return "clip-" + d.id; })
    .append("use")
      .attr("xlink:href", function(d) { return "#rect-" + d.id + ""; });

  var label = cell.append("text")
      .attr("clip-path", function(d) { return "url(#clip-" + d.id + ")"; });

  label
    .filter(function(d) { return d.children; })
    .selectAll("tspan")
      .data(function(d) { return d.id.substring(d.id.lastIndexOf(".") + 1).split(/(?=[A-Z][^A-Z])/g).concat("\xa0" + format(d.value)); })
    .enter().append("tspan")
      .attr("x", function(d, i) { return i ? null : 4; })
      .attr("y", 13)
      .text(function(d) { return d; });

  label
    .filter(function(d) { return !d.children; })
    .selectAll("tspan")
      .data(function(d) { return d.id.substring(d.id.lastIndexOf(".") + 1).split(/(?=[A-Z][^A-Z])/g).concat(format(d.value)); })
    .enter().append("tspan")
      .attr("x", 4)
      .attr("y", function(d, i) { return 13 + i * 10; })
      .text(function(d) { return d; });

  cell.append("title")
      .text(function(d) { return d.id + "\n" + format(d.value); });
      

function hovered(hover) {
  return function(d) {
    d3.selectAll(d.ancestors().map(function(d) { return d.node; }))
        .classed("node--hover", hover)
      .select("rect")
        .attr("width", function(d) { return d.x1 - d.x0 - hover; })
        .attr("height", function(d) { return d.y1 - d.y0 - hover; });
  };
};


</script>

